Multi-product Batch Processing Time Maximization Problem

### 2023-07-05 (2023) Fraga et al.tex
updating paper

%%Research highlights
\begin{highlights}
\item this paper presents a brief bibliographic review on multi-product batch problems;
\item presents a new combinatorial optimization problem named Multi-product Batch Processing Time Maximization (MPBPTM) problem;
\item presents a linear integer programming model for the MPBPTM problem;
\item proposes a polynomial time analytical method for solving the MPBPTM problem.
\end{highlights}

@@

The scientific literature presents several papers that address multi-product batch problems. Many works target the problem of multi-product batch scheduling (MPBS), in which it is necessary to determine the production sequence of the products and the ideal batch size for each product, in a production of several products which share the same production facilities and for which demand is known \citep{Eilon1985}. In this problem, a single product is processed at a time, so it is necessary that the quantity produced is sufficient to meet the demand during the period in which other products are being processed. The solution must be determined in such a way that both setup and storage costs are minimized. Among the authors who addressed this problem are \cite{Eilon1985}, \cite{Omega1993} and \cite{LiuEtAl2020}. \cite{MendezEtAll2000} and \cite{ShiEtAll2017} deal with a parallel multi-product batch scheduling  (PMPBS) problem, in which production units of the same type are arranged in parallel, forming each production stage. In this case, it is also necessary to define in which units each product will be processed. The authors also take into account other constraints for the problem (\emph{e.g.}, release time and due date for the products, and sequencing constraints due to mismatched product colors sequences) and other goals (\emph{i.e.}, optimize customer satisfaction and/or the plant performance). In the papers mentioned above, production in a single unit or in a serial flowshop plant is considered, in which all products follow a linear flow through the production stages. \cite{KimEtAl1996} consider the multi-product batch problem in networked processes. As defined by the authors, in this case, the production units are not arranged in lines, and the connection between the units may or may not exist. Therefore, the production paths in the flowshop network can be different for each product. Also the passing of previous batch can be possible so that the final sequence of the production at the last stage units can be different from the initial sequence. Other important works deal with the problem of a multi-product batch plant design (MPBPD). In this case the problem is to obtain the configuration of the plant and the equipment that minimize the capital cost of all the equipment items needed to fulfill the production requirements \citep{RavemarkAndRippin1998}.

In this work, we are concerned with determining the ideal processing time for a batch consisting of a set of products, each product being or not different from the other products of the same batch. That is, we consider a specific case where different products are processed simultaneously on the same processor. This case occurs, for example, during the processing of plastic bags in extruders, where the resins are melted, then pass through a cylinder forming a balloon and this balloon, after cooling, is stored in a coil which, in turn, is cut into several smaller coils, forming different models of plastic bags.

As scientific contributions, in this paper we define a new multi-product batch problem, named multi-product batch processing time maximization (MPBPTM) problem, as well as a mathematical model and an analytical solution method for solving this problem.

In the next sections, a presentation of problem is made along with an application example. Section \ref{sec:mathModel} presents an interger linear mathematical model for the problem and section \ref{sec:analyticalSol} presents an analytical method for its solution. Section \ref{sec:results} presents the tests and results obtained by a solver in C++ applying the analytical solution and a solver developed in LINGO to new proposed benchmarks. In sections \ref{sec:contributions} and \ref{sec:acknowledgments}, the contributions for this work are informed and acknowledgments are given, respectively. Finally, section \ref{sec:conclusions} presents the paper's conclusions and suggestions for future works.

@@

The multiproduct batch processing time maximization problem arises when a set of different products are processed simultaneously in a same production batch. In this problem, it is considered that the quantity produced of each product is directly proportional to the processing time, however, with a different proportionality rate (prodction rate) for each product. In addition, there is a maximum quantity allowed for the production of batch products, defined both individually and for the set. The maximum production quantity of each product is mainly defined according to the demand for the product. However, it is still possible to stock the products and/or send them to the outlets. In both cases, there is a stocking/shipping limit for each product and a stocking/shipping limit for the set of products in the batch. Also, there is a time limit available for processing the batch. The problem consists of defining the maximum processing time for the batch, respecting the limitations related to the quantities produced. For a better understanding of the problem, an example is presented below.

@@

Note that it is not important to know the values of $O_i$ and $I_i$, $\forall i$, however, after determining a solution, these values can be found by taking a solution from the indeterminated system of inequations:

>>>>

%%Research highlights
\begin{highlights}
\item brief bibliographic review on multi-product batch problems;
\item new combinatorial optimization problem named Multi-product Batch Processing Time Maximization (MPBPTM) problem;
\item linear integer programming model for the MPBPTM problem;
\item polynomial time complexity analytical method for solving the MPBPTM problem.
\end{highlights}

@@

The scientific literature presents several papers that address multi-product batch problems. Many works target the problem of multi-product batch scheduling (MPBS), in which it is necessary to determine the production sequence of the products and the ideal batch size for each product, in a production of several products which share the same production facilities and for which demand is known \citep{Eilon1985}. In this problem, a single product is processed at a time, so it is necessary that the quantity produced is sufficient to meet the demand during the period in which other products are being processed. The solution must be determined in such a way that both setup and storage costs are minimized. Among the authors who addressed this problem are \cite{Eilon1985}, \cite{Omega1993} and \cite{LiuEtAl2020}. \cite{MendezEtAll2000} and \cite{ShiEtAll2017} present two parallel multi-product batch scheduling (PMPBS) problems, in which production units of the same type are arranged in parallel, forming each production stage. In this case, it is also necessary to define in which units each product will be processed. The authors also take into account other constraints for the problem (\emph{e.g.}, release time and due date for the products, and sequencing constraints due to mismatched product colors sequences) and other goals (\emph{i.e.}, optimize customer satisfaction and/or the plant performance). In the papers mentioned above, production in a single unit or in a serial flowshop plant is considered, in which all products follow a linear flow through the production stages. \cite{KimEtAl1996} consider the multi-product batch problem in networked processes. As defined by the authors, in this case, the production units are not arranged in lines, and the connection between the units may or may not exist. Therefore, the production paths in the flowshop network can be different for each product. Also the passing of previous batch can be possible so that the final sequence of the production at the last stage units can be different from the initial sequence. Other important works deal with the problem of a multi-product batch plant design (MPBPD). In this case the problem is to obtain the configuration of the plant and the equipment that minimize the capital cost of all the equipment items needed to fulfill the production requirements \citep{RavemarkAndRippin1998}.

In this work, we are concerned with determining the ideal processing time for a batch consisting of a set of products, each product being or not different from the other products of the same batch. That is, we consider a specific case where different products are processed simultaneously on the same processor. This case occurs, for example, during the processing of plastic bags in extruders, where the resins are melted, then pass through a cylinder forming a balloon and this balloon, after cooling, is stored in a coil which, in turn, is cut into several smaller coils with different models of plastic bags.

As scientific contributions, in this paper we define a new multi-product batch problem, named multi-product batch processing time maximization (MPBPTM) problem, as well as a mathematical model and a polynomial time complexity analytical solution method for solving this problem.

In the next sections, a presentation of problem is made along with an application example. Section \ref{sec:mathModel} presents an interger linear mathematical model for the problem and section \ref{sec:analyticalSol} presents an analytical method for its solution. Section \ref{sec:results} presents the tests and results obtained by a solver in C++ applying the analytical solution and a solver developed in LINGO to new proposed benchmarks. In sections \ref{sec:contributions} and \ref{sec:acknowledgments}, the contributions to this work are informed and acknowledgments are given, respectively. Finally, section \ref{sec:conclusions} presents the paper's conclusions and suggestions for future works.

@@

The multiproduct batch processing time maximization problem arises when a set of different products are processed simultaneously in a same production batch. In this problem, it is considered that the quantity produced of each product is directly proportional to the processing time, however, with a different constant of proportionality (prodction rate) for each product. In addition, there is a maximum quantity allowed for the production of batch products, defined both individually and for the set. The maximum production quantity of each product is mainly defined according to the demand for the product. However, it is still possible to stock the products and/or send them to the outlets. In both cases, there is a stocking/shipping limit for each product and a stocking/shipping limit for the set of products in the batch. Also, there is a time limit available for processing the batch. The problem consists of defining the maximum processing time for the batch, respecting the limitations related to the quantities produced. For a better understanding of the problem, an example is presented below.

@@

Note that it is not important to know the values of $O_i$ and $I_i$, $\forall i$, however, after determining a solution, these values can be found by taking a solution from the undetermined system of inequalities:
